|

### 2022-10-05 manuscript_BE/manuscript_BE.Rmd
Edits to include PAA in the analysis. As well as first attempt to use BayesianTools in the MCMC

scen1<-"MCMCclean_gam_Nrew_sca_"
scen2<-"MCMCclean_gam_sca_"
scen3<-"MCMCclean_Nrew_sca_"
scen4<-"MCMCclean_PAA_gam_Nrew_sca_"
scen5<-"MCMCclean_PAA_gam_sca_"
scen6<-"MCMCclean_PAA_Nrew_sca_"

@@

scen1<-"MCMCclean_gam_Nrew_sca_"
scen2<-"MCMCclean_gam_sca_"
scen3<-"MCMCclean_Nrew_sca_"
 source(here("predictions.R"))
first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
           rel_heights = c(1.4,1,1),
          labels=c('b','d','f'))
plot_grid(first_col,second_col,rows = 1)
```

@@

source(here("predictions.R"))
first_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
          cont.obs.pred.both,cont.obs.pred.gam,cont.obs.pred.Nrew,
          labels=c('a','c','e'),rel_heights = c(1.4,1,1))
second_col<-plot_grid(nrow=3,align = "v",byrow = TRUE,
                      rel_heights = c(1.4,1,1),
          scatter.obs.pred.both,scatter.obs.pred.gam,scatter.obs.pred.Nrew,
          labels=c('b','d','f'))
plot_grid(first_col,second_col,rows = 1)
```

>>>>

scen1<-"MCMCclean_gam_Nrew_sca_"
scen2<-"MCMCclean_gam_sca_"
scen3<-"MCMCclean_Nrew_sca_"
scen4<-"MCMCclean_PAA2_gam_Nrew_sca_"
scen5<-"MCMCclean_PAA2_gam_sca_"
scen6<-"MCMCclean_PAA2_Nrew_sca_"

@@

scen1<-"MCMCclean_gam_Nrew_sca_"
scen2<-"MCMCclean_gam_sca_"
scen3<-"MCMCclean_Nrew_sca_"
 source(here("predictions.R"))
first_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
          cont.obs.pred.both,cont.obs.pred.gam,
          labels=c('a','c'),rel_heights = c(1.4,1))
second_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
          cont.obs.pred.Nrew,scatter.all.plot,
           rel_heights = c(1,1.4),
          labels=c('b','d'))
plot_grid(first_col,second_col)
```

@@

source(here("predictions.R"))

first_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
          cont.obs.pred.both,cont.obs.pred.gam,
          labels=c('a','c'),rel_heights = c(1.4,1))
second_col<-plot_grid(nrow=2,align = "v",byrow = TRUE,
          cont.obs.pred.Nrew,scatter.all.plot,
           rel_heights = c(1,1.4),
          labels=c('b','d'))
plot_grid(first_col,second_col)
```
